A New Model to Predict Survival in Patients with End-Stage Liver Disease

### 2022-06-16 analysis/article.Rmd
fix: don't echo code chunks

```{r survivalcalc, results = "asis"}
cfnmsltx <- paste0("\\text{", gsub(" ", "\\ ", cfnms), "}")
cat(
    "$$\\begin{align}",
    "S &= S_{0,90}^{\\exp{LP}} \\\\",
    "&= ", round(s0["90"], 4), "^{\\exp{(",
        paste0(
            round(cfs[1], 4), " * zlog(", cfnmsltx[1], ")",
            paste0(
                ifelse(sign(cfs[-1]) > 0, "+", ""),
                round(cfs[-1], 4), " * zlog(", cfnmsltx[-1], ")",
                collapse = ""
            ),
            collapse = ""
        ),
    ")}}"
)
```
(\#eq:survcalc)
\end{align}
$$
<!-- using eq:survcalc inside the R code chunk impedes Math ML rendering -->

@@

```{r roctest}
tp <- timeROC::compare(
    timeROC_RCV, timeROC_MELDNa,
    adjusted = TRUE
)$p_values_AUC
rownames(tp) <- paste(
    c("Non-adjusted", "Adjusted"), "$p$-values"
)
knitr::kable(
    tp,
    caption = paste0(
        "Test comparison between AUCROC for MELD-Na and AMELD",
        "according to @blanche2013 at day ",
        paste0(timeROC_RCV$times, collapse = ", "), ".",
        "$p$-values are shown as non-adjusted and adjusted for ",
        "multiple testing."
    ),
    digits = 2
)
```

>>>>

```{r survivalcalc, results = "asis", echo = FALSE}
cfnmsltx <- paste0("\\text{", gsub(" ", "\\ ", cfnms), "}")
cat(
    "$$\\begin{align}",
    "S &= S_{0,90}^{\\exp{LP}} \\\\",
    "&= ", round(s0["90"], 4), "^{\\exp{(",
        paste0(
            round(cfs[1], 4), " * zlog(", cfnmsltx[1], ")",
            paste0(
                ifelse(sign(cfs[-1]) > 0, "+", ""),
                round(cfs[-1], 4), " * zlog(", cfnmsltx[-1], ")",
                collapse = ""
            ),
            collapse = ""
        ),
    ")}}"
)
```
(\#eq:survcalc)
\end{align}
$$
<!-- using eq:survcalc inside the R code chunk impedes Math ML rendering -->

@@

```{r roctest, echo = FALSE}
tp <- timeROC::compare(
    timeROC_RCV, timeROC_MELDNa,
    adjusted = TRUE
)$p_values_AUC
rownames(tp) <- paste(
    c("Non-adjusted", "Adjusted"), "$p$-values"
)
knitr::kable(
    tp,
    caption = paste0(
        "Test comparison between AUCROC for MELD-Na and AMELD",
        "according to @blanche2013 at day ",
        paste0(timeROC_RCV$times, collapse = ", "), ".",
        "$p$-values are shown as non-adjusted and adjusted for ",
        "multiple testing."
    ),
    digits = 2
)
```
